fGFPCA dynamic prediction (In-sample)

### 2022-12-01 f-GFPCA.Rmd
edit report

```{r}
df %>% 
  filter(id %in% 1:4) %>% 
  mutate(probs = exp(eta_i)/(1+exp(eta_i))) %>%
  ggplot()+
  geom_line(aes(x=sind, y=eta_i), col = "blue")+
  geom_line(aes(x=sind, y=probs), col = "red")+
  geom_point(aes(x=sind, y=Y), size = 0.05)+
  facet_wrap(~id)+
  labs(title = "Four simulated subjects")
```

@@

```{r}
ggplot(df_pred_latent %>% filter(id %in% 1:4))+
  geom_line(aes(x = sind_inx, y=eta_hat))+
  geom_line(aes(x=sind_inx, y = eta_i, col = "red"))+
  # geom_point(aes(x=sind_inx, y = Y, col = "blue"), size = 0.01)+
  facet_wrap(~id)+
  labs(title = "Predicted latent functions on original grid")
```
```{r}
df_pred_latent %>% filter(id %in% 1:4 & sind_inx %in% mid) %>%
  ggplot()+
  geom_line(aes(x = sind_inx, y=eta_hat))+
  geom_line(aes(x=sind_inx, y = eta_i, col = "red"))+
  # geom_point(aes(x=sind_inx, y = Y, col = "blue"), size = 0.01)+
  facet_wrap(~id)+
  labs(title = "Predicted latent functions on binned grid")

@@

```{r}
## mean functions
plot(mid, fpca_fit$mu, ylab = "mean")
```

@@

Below we try to do that with one subject:

- Subject 1

>>>>

```{r}
df %>% 
  filter(id %in% 1:4) %>% 
  mutate(probs = exp(eta_i)/(1+exp(eta_i))) %>%
  ggplot()+
  geom_line(aes(x=sind, y=eta_i, color = "True Gaussian function"))+
  geom_line(aes(x=sind, y=probs, color = "Probability scale"))+
  geom_point(aes(x=sind, y=Y, color = "Binary outcome"), size = 0.05)+
  facet_wrap(~id)+
  labs(title = "Four simulated subjects", color = "Legend")+
  scale_color_manual(values = c("True Gaussian function" = "blue", "Probability scale" = "red", "Binary outcome" = "black"))
```

@@

```{r}
ggplot(df_pred_latent %>% filter(id %in% 1:4))+
  geom_line(aes(x = sind_inx, y=eta_hat, color = "Estimated"))+
  geom_line(aes(x=sind_inx, y = eta_i, color = "True"))+
  facet_wrap(~id)+
  labs(title = "Predicted latent functions on original grid", color = "Lgend")+
  scale_color_manual(values = c("Estimated" = "red", "True" = "Black"))
```
```{r}
df_pred_latent %>% filter(id %in% 1:4 & sind_inx %in% mid) %>%
  ggplot()+
  geom_line(aes(x = sind_inx, y=eta_hat, col = "Estimated"))+
  geom_line(aes(x=sind_inx, y = eta_i, col = "True"))+
  # geom_point(aes(x=sind_inx, y = Y, col = "blue"), size = 0.01)+
  facet_wrap(~id)+
  labs(title = "Predicted latent functions on binned grid", color = "Lgend")+
  scale_color_manual(values = c("Estimated" = "red", "True" = "Black"))
```

@@

```{r, fig.height=4, fig.width=4}
## mean functions
plot(mid, fpca_fit$mu, ylab = "mean")
```

@@

Below we try to do that with a few subjects:
